Open-Set Domain Adaptation through Self-Supervision

### 2022-02-13 paper/main.tex
Updated sections

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{caption}
% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}
\usepackage{multirow}
\usepackage{float}

@@

\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
Politecnico di Torino\\
Italy\\
{\tt\small \{s286302,s292477,s292459,292435\}@studenti.polito.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  In machine learning applications, domain adaptation (DA) techniques try to mitigate the problem of having different domains in the training and test data.
  Another common problem is represented by the presence of more semantic classes in the test data, which are unknown
  and completely new to the developed models. The latter problem comes under the name of novelty or anomaly detection.
  In real world scenarios, it is becoming extremely common suffering of both problems.
  \textit{Open-Set Domain Adaptation (OSDA)} methods try to tackle these problems by jointly adapting a model trained on a labeled source domain to an unlabeled target domain
  while performing novelty detection. We propose a new method leveraging a self-supervised technique, rotation recognition, constisting in first performing
  novelty detection on the target data and then aligning the two domains avoiding potential negative adaptation.
  Furthermore, we assess the performance using a new metric which represents in a balanced way the ability to jointly solve the two problems.
  Experiments conducted on the Office-Home benchmark show interesting results and method effectiveness.

  % Performance loss over domain change is a common problem in machine learning applications.
  % Solving the issue usually relies on adapting the model to the new domain by having at disposal large and labeled datasets, either rare or costly to acquire.
  % In this paper we propose a new approach, adapting models to the new domains while not needing relying on labeled data thanks to a self-supervision.
  % Experiments conducted on the Office-Home dataset show interesting results and method effectiveness.
\end{abstract}

@@

One of the problems which is causing this loss of performance is the domain gap between the training data and the actual observed data. Intuitively, if we train a model on a specific domain,
such as employing real world pictures depicting real objects, for example to perform classification, we expect that the model will perform well on a fairly large variety of test cases.
However, the actual data present a huge variety on the domains while still representing the same semantic classes that we want to predict.
For example, we may want to be capable of predicting that both an image of a real elephant and a drawing of an elephant are containing the semantic class \textit{elephant}.
Domain adaptation techniques have been developing in recent years to reduce the domain gap between a labeled source domain and one or more unlabeled target domains.
Generally, this is done by enforcing the learning of domain-invariant patterns of both domains.
As underlined in \cite{domainAdaptFarahani}, this is usually achieved by learning a transformation function which projects both the source and target domain data in a
new space where we jointly maintain the underlying structure of the original data while reducing the domain gap by removing the domain-specific information.

Another big issue encountered in real world usages is the presence of additional anomaly semantic classes on the observed data.
The problem comes under the name of \textit{Open-Set Recognition (OSR)} \cite{OSRsurvey}, where we require not only to accurately classify the known seen classes, but also
effectively deal with unknown ones, which would otherwise drastically weaken the robustness of the methods.

The jointly presence and accounting of the two described problems has been emerged as a new sub-field of computer vision with the name of \textit{Open-Set Domain Adaptation (OSDA)}.
As a consequence, if we try to reduce the domain gap between the whole target domain and the source domain, we will observe a negative adaptation due to the unwanted alignment between
the data belonging to the anomaly semantic classes and the source classes we want to model and predict.
For this reason, it is important to first perform anomaly detection of the additional set of novelty classes, translating the problem into a \textit{Closed-Set Domain Adaptation (CSDA)} one,
and next do the alignment between the source and the target domain identified as known.

Common machine learning methods usually leverage huge manually annotated datasets to perform well on the given tasks.
However, acquiring annotated material is usually very costly and difficult, moreover, relying on such data may not be scalable in large applications on the long run.
Thus, recently, a commonly employed approach is self-supervised learning, which consists in creating new automatically labeled data starting from the original unlabeled data.
The fundamental idea is creating some auxiliary task from input data so that,
by solving such task, the model can learn the underlying structure of the data,
for instance high-level knowledge, correlations, and metadata embedded.
This type of learning has been recently used for Domain Adaptation, 
learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,GeoTran}.

The approach presented in this paper combines the power of the self-supervised learning with the standard supervised learning approach for semantic class recognition.
A two-stage method is hence proposed, 
aiming to identify and isolate unknown class samples in the first stage, 
before reducing in the second stage the domain gap between the source domain and the known target domain to avoid negative transfer.
This is done in both stages using a modified version of the rotation task as self-supervised method,
predicting the relative rotation between an image and its rotated version.
Finally, a classifier is used to predict if each target sample belongs either to one of the knwon classes or to an unknown class, 
being rejected in the latter case.
We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} exploiting a new OSDA metric.

@@

The problem was first formulated in \cite{firstPaperOSR} and since then, several other works have analyzed this challenge in the context 
of deep networks \cite{perera2019deep, hein2019relu, bendale2015open}.
Some techinques presented in the past were focus on an adversarial approach to 
delineate closed from open-set images \cite{ge2017generative, kong2021opengan}.
Other approaches include reconstruction based methods 
\cite{yoshihashi2019classificationreconstruction}
which use poor test-time reconstruction as an open-set indicator.

@@

\textbf{Self-supervised Learning} is an emerging field focused on using 
data itself as supervision for auxiliary (also called “pretext”) 
tasks that learn deep feature representations, which will hopefully be informative 
for downstream “real” tasks.
Many such auxiliary tasks have been proposed in the literature, including
image colorization \cite{zhang2016colorful},
image jigsaw puzzle [\cite{noroozi2017unsupervised}, image inpainting \cite{pathak2016context},
contrastive learning \cite{oord2019representation}, geometric transformations \cite{dosovitskiy2015discriminative}.

@@

Table \ref{tab:results} contains the results for all 12 available domain shifts,
as well as perfomance differences when using multi-head rotation classifiers and center loss,
as described in the previous section.
Multi-headed models are more capable of correctly discriminating between known and unknown samples,
ultimately resulting in better domain alignment.
This effect is amplified when also using center loss.
AUROC values are computed at the end of the separation stage, 
while HOS values are sampled at regular times on the entire original target dataset.

\subsection{Ablation Study}
\label{sec:ablation_study}
As shown in table \ref{tab:results} different architectures give different results, 
and as shown in image \ref{fig:hyperparams} each one requires a different set of parameters.
To choose optimal parameters a sequential approach is followed, 
by optimizing one parameter at the time.
The order of optimization followed is: 
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run on two domain shifts, 
Art $\to$ Clipart and Clipart $\to$ Product.
In appendix \ref{sec:tables} we report the steps followed for each configuration.

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks.
A few critical points still remain on our method of study and proposed solution.
The most important one is probably parameter choosing for different models, as we have seen that variations cause huge differences in results and sequential optimization of parameter is a sub-optimal heuristic.
Furthermore, having the model to learn two different tasks at once, it could be useful to use a slower learning model at the expense of longer training times.
Another observation that we can make based 
on gathered data is the impact that the threshold 
choice have during the target separation step.
This is ascrivable to a weak normality score 
that may need particular attention in order to develop
a model able to reduce negative transfer.

@@

\begin{table}[hb!]
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyper-parametr optimization process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

\begin{table}[t!]
  \vspace{-1.7cm}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{ON-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
    3.0  & & & 38.45\% \\
    5.0  & & & 37.61\% \\
    10.0 & & & 33.23\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
    & 0.45 & & 42.40\% \\
    & 0.5 & & 43.48\% \\
    & 0.55 & & 46.21\% \\
    & {\bf0.6} & & {\bf 50.17\%} \\
    & 0.65 & & 45.82\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
    && 1.0 & 47.71\% \\
    && 2.0 & 46.56\% \\
    && {\bf 3.0} & {\bf 50.17\%} \\
    && 4.0 & 46.57\% \\
    && 5.0 & 47.52\% \\
    && 10.0 & 44.56\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonoff} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss Off}
\end{table}

\begin{table}[hb!]
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{ON-ON} \\
    \hline
    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
    {\bf 3.0} & && & {\bf 45.33\%} \\
    5.0 & && & 42.41\% \\
    10.0 & && & 37.15\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
    \hline
    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
    & 0.001 & & & 36.71\% \\
    & 0.01 & & & 45.33\% \\
    & {\bf 0.05 }& & & {\bf 46.63\%} \\
    & 0.1 & & & 37.44\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
    & & 0.45 & & 45.13\% \\
    & & 0.5 & & 46.63\% \\
    & & 0.55 & & 47.09\% \\
    & & {\bf 0.6} & & {\bf 49.78\%} \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
    & & & 1.0 & 45.23\% \\
    & & & 2.0 & 45.76\% \\
    & & & {\bf 3.0} & {\bf 49.78\%} \\
    & & & 4.0 & 46.20\% \\
    & & & 5.0 & 48.60\% \\
    & & & 10.0 & 44.14\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonon} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss On}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & 27.94 & 68.13 & 17.58 & 52.25 & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & 58.64 & 46.81 & 60.95 & 37.99 \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 52.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Final results for the three configurations on all domain shifts. All values are percentages.}
\end{table*}

>>>>

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{caption}
% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}
\usepackage{multirow}
\usepackage{float}
\usepackage{url}

@@

\author{Protopapa Andrea, Quarta Matteo, Ruggeri Giuseppe, Versace Alessandro\\
Politecnico di Torino\\
Italy\\
{\tt\small s\{286302,292477,292459,292435\}@studenti.polito.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  In machine learning applications, domain adaptation (DA) techniques try to mitigate the problem of having different domains in the training and test data.
  Another common problem is represented by the presence of more semantic classes in the test data, which are unknown
  and completely new to the developed models. The latter problem comes under the name of novelty or anomaly detection.
  In real world scenarios, it is becoming extremely common suffering of both problems.
  \textit{Open-Set Domain Adaptation (OSDA)} methods try to tackle these problems by jointly adapting a model trained on a labeled source domain to an unlabeled target domain
  while performing novelty detection. We propose a new method leveraging a self-supervised technique, rotation recognition, constisting in first performing
  novelty detection on the target data and then aligning the two domains avoiding potential negative adaptation.
  Furthermore, we assess the performance using a new metric which represents in a balanced way the ability to jointly solve the two problems.
  Experiments conducted on the Office-Home benchmark show interesting results and method effectiveness.
  Full code for our proposed method is made publicly available \url{https://github.com/coccocarmiano/AML2021}
\end{abstract}

@@

One of the problems which is causing this loss of performance is the domain gap between the training data and the actual observed data. Intuitively, if we train a model on a specific domain,
such as employing real world pictures depicting real objects, for example to perform classification, we expect that the model will perform well on a fairly large variety of test cases.
However, the actual data present a huge variety on the domains while still representing the same semantic classes that we want to predict.
For example, we may want to be capable of predicting that both an image of a real elephant and a drawing of an elephant are containing the semantic class \textit{elephant}.
Domain adaptation techniques have been developing in recent years to reduce the domain gap between a labeled source domain and one or more unlabeled target domains.
Generally, this is done by enforcing the learning of domain-invariant patterns of both domains.

Another big issue,
named {\textit Open-Set Recognition (OSR)} \cite{OSRsurvey},
features the presence of additional anomalous semantic classes in the observed data and requires to both accurately classify
known observed samples and also reject the ones from unknown classes.

The joint presence and accounting of these two problems has been formalized as a new sub-field of computer vision with the name of \textit{Open-Set Domain Adaptation (OSDA)}.
As a consequence, 
if we try to reduce the domain gap between the whole target and the source domain, 
we will observe an unwanted alignment between
the data belonging to anomalous semantic classes and the source classes we want to model and predict.
For this reason, 
it is important to first perform anomaly detection of the additional set of unknown classes
and then do the alignment between the source and the target domain identified as known
translating the problem into a \textit{Closed-Set Domain Adaptation (CSDA)} one.

Common machine learning methods usually leverage huge manually annotated datasets to perform well on the given tasks.
However, 
acquiring such data is often very costly and relying on this data may not be scalable in large applications on the long run.
Recently, 
a commonly employed approach is self-supervised learning, 
which consists in creating new automatically labeled data starting from the original unlabeled data.
The fundamental idea is creating some auxiliary task from input data so that the model can learn the underlying structure of the data,
such as high-level knowledge, correlations, and metadata embedded.
This type of learning has been recently used for Domain Adaptation, 
learning robust cross-domain features and supporting generalization \cite{CarlucciJigsaw,SelfSupervisedXu},
and also for some Open Set problems specialized in anomaly detection and discriminating anomalous data \cite{bergman2020classificationbased,GeoTran}.

The approach presented in this paper combines the power of the self-supervised learning with the standard supervised learning approach for semantic class recognition.
We propose a two stage method aiming to identify and isolate unknown class samples in the first stage, 
and reducing the domain gap between domains in the second stage to avoid negative transfer.
This is done by using a modified version of the rotation task as self-supervised method,
predicting the relative rotation between an image and its rotated version.
Finally, a classifier is used to predict if each target sample belongs to either one of the knwon classes or to an unknown class, 
being rejected in the latter case.
We evaluate the method on the Office-Home benchmark \cite{OfficeHomeDataset} using a new OSDA metric.

@@

The problem was first formulated in \cite{firstPaperOSR} and since then, several other works have analyzed this challenge in the context 
of deep networks \cite{perera2019deep, hein2019relu, bendale2015open}.
Some techinques presented in the past were focus on an adversarial approach to 
delineate closed from open-set images \cite{ge2017generative, kong2021opengan}.

@@

\textbf{Self-supervised Learning} is an emerging field focused on using 
data itself as supervision for auxiliary (also called “pretext”) 
tasks that learn deep feature representations, which will hopefully be informative 
for downstream “real” tasks.
Many such auxiliary tasks have been proposed in the literature, including
image colorization \cite{zhang2016colorful},
image jigsaw puzzle [\cite{noroozi2017unsupervised}, geometric transformations \cite{dosovitskiy2015discriminative}.

@@

Table \ref{tab:results} contains the results for all 12 available domain shifts,
as well as perfomance differences when using multi-head rotation classifiers and center loss,
as described in the previous section.
Multi-headed models are more capable of correctly discriminating between known and unknown samples,
ultimately resulting in better domain alignment.
This effect is amplified when also using center loss.
AUROC and HOS values are taken at the end of the relative stages.

\subsection{Ablation Study}
\label{sec:ablation_study}
Image \ref{fig:hyperparams} summarizes the parameter optimization process where a sequential approach is followed.
For each configuration one hyper-parameter is optimized at a time,
following the order
$\alpha_1$, $\lambda_1$, $\mathcal{\tilde N}$, $\alpha_2$ and picking the parameter giving the highest HOS.
Models not using center loss just skip the $\lambda_1$ optimization.
Ablation study were run on two domain shifts, 
Art $\to$ Clipart and Clipart $\to$ Product.
In appendix \ref{sec:tables} tables \ref{tab:ablationoffoff}, \ref{tab:ablationonoff} and \ref{tab:ablationonon} report all the steps followed for each configuration.
This information is also summarized in figure \ref{fig:hyperparams}.
We can notice that most of the optimal parameters are shared between configurations,
an exception being the normality score $\mathcal{\tilde N}$ on a single-headed configuration.
This is due to the fact that having to use only one head for all classes it is better to be very confident about classyfing a sample as known.
Smaller $\alpha_1$ and $\alpha_2$ values are preferred as they avoid overfitting the rotation classifiers as the object classifiers take a longer time to converge.
As center loss contributions are directly summed to the rotation classifier loss term while being much bigger, 
much smaller values need to be used for a correct model convergence.

@@

The results show that self-supervision technique can help in domain adaptation task and open-set classification tasks,
but some critical points still remain in our method of study and proposed solution.
The most important one is probably the parameter optimization method for different models,
as small variations can cause huge differences in results sequentially optimizing hyper-parameters is a sub-optimal heuristic.
Furthermore,
having models learn different tasks simultaneosly can lead to instability, 
so using slower learning models at the expense of longer training times can improve results.
A criticality is represented by the normality score hyper-parameter:
model confidence over accepting or rejecting a sample is very thight between known and unknwon samples,
so a better function do have more spread scores can bring more efficient separation,
ultimately resulting in a better quality input data in the second step.
Last,
center loss function relies on learning centroids based on sample features to predict rotation.
This formulation requires picking a specific learning rate for such centroids,
but we didn't run any test on how such learning rate impacts predictions or sample separability.

@@

\begin{table}[h!]
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{OFF-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 40.27\%} \\
    3.0  & & & 22.69\% \\
    5.0  & & & 18.78\% \\
    10.0 & & & 9.99\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.50 & \multirow{6}{*}{3.0}  & 28.05\%\\
    & 0.55 & & 34.73\% \\
    & 0.60 & & 40.27\% \\
    & 0.65 & & 43.16\% \\
    & {\bf 0.70} & & {\bf 44.38\%} \\
    & 0.75 & & 43.87\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 42.79\%\\
    && 1.0 & 44.35\% \\
    && 2.0 & 43.53\% \\
    && {\bf 3.0} & {\bf 44.38}\% \\
    && 4.0 & 43.12\% \\
    && 5.0 & 41.97\% \\
    && 10.0 & 42.01\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationoffoff} Hyper-parametr optimization process for configuration Multi-Head Off and Center-Loss Off}
\end{table}

\begin{table}[t!]
  \vspace{-2cm}
  \centering
  \begin{tabular}[h]{||c|c|c||c||}
    \hline
    \multicolumn{4}{||c||}{ON-OFF} \\
    \hline
    $\alpha_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$\\    
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_1$} \\
    \hline
    {\bf 1.0}  & \multirow{4}{*}{0.6} & \multirow{4}{*}{3.0} & {\bf 43.48\%} \\
    3.0  & & & 38.45\% \\
    5.0  & & & 37.61\% \\
    10.0 & & & 33.23\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{6}{*}{1.0} & 0.4 & \multirow{6}{*}{3.0}  & 38.40\%\\
    & 0.45 & & 42.40\% \\
    & 0.5 & & 43.48\% \\
    & 0.55 & & 46.21\% \\
    & {\bf0.6} & & {\bf 50.17\%} \\
    & 0.65 & & 45.82\% \\
    \hline
    \hline
    \multicolumn{4}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{1.0} & \multirow{7}{*}{0.7} & 0.1 & 46.02\%\\
    && 1.0 & 47.71\% \\
    && 2.0 & 46.56\% \\
    && {\bf 3.0} & {\bf 50.17\%} \\
    && 4.0 & 46.57\% \\
    && 5.0 & 47.52\% \\
    && 10.0 & 44.56\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonoff} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss Off}
\end{table}

\begin{table}[b!]
  \centering
  \begin{tabular}[h]{||c|c|c|c||c||}
    \hline
    \multicolumn{5}{||c||}{ON-ON} \\
    \hline
    $\alpha_1$ & $\lambda_1$ & $\mathcal{\tilde N}$ & $\alpha_2$ & HOS$_{mean}$ \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_1$} \\
    \hline
    1.0 & \multirow{4}{*}{0.01} & \multirow{4}{*}{0.05} & \multirow{4}{*}{3.0} & 44.90\% \\
    {\bf 3.0} & && & {\bf 45.33\%} \\
    5.0 & && & 42.41\% \\
    10.0 & && & 37.15\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\lambda_1$} \\
    \hline
    \multirow{5}{*}{3} & 0.0001 & \multirow{5}{*}{0.5} & \multirow{5}{*}{3.0} & 39.90\% \\
    & 0.001 & & & 36.71\% \\
    & 0.01 & & & 45.33\% \\
    & {\bf 0.05 }& & & {\bf 46.63\%} \\
    & 0.1 & & & 37.44\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\mathcal{\tilde N}$} \\
    \hline
    \multirow{5}{*}{3} & \multirow{5}{*}{0.05} & 0.4 & \multirow{5}{*}{3.0} & 44.32\% \\
    & & 0.45 & & 45.13\% \\
    & & 0.5 & & 46.63\% \\
    & & 0.55 & & 47.09\% \\
    & & {\bf 0.6} & & {\bf 49.78\%} \\
    & & 0.65 & & 47.23\% \\
    \hline
    \hline
    \multicolumn{5}{||c||}{Picking $\alpha_2$} \\
    \hline
    \multirow{7}{*}{3} & \multirow{7}{*}{0.05} & \multirow{7}{*}{0.6} & 0.1 & 45.73\% \\
    & & & 1.0 & 45.23\% \\
    & & & 2.0 & 45.76\% \\
    & & & {\bf 3.0} & {\bf 49.78\%} \\
    & & & 4.0 & 46.20\% \\
    & & & 5.0 & 48.60\% \\
    & & & 10.0 & 44.14\% \\
    \hline
  \end{tabular}
  \caption{\centering\label{tab:ablationonon} Hyper-parameters optimization process for configuration Multi-Head On and Center-Loss On}
\end{table}

\begin{table*}
  \centering
  \begin{tabular}[t]{||c||c|c|c|c||c|c|c|c||c|c|c|c||}
    \hline
    \multicolumn{13}{||c||}{Results} \\
    \hline
    \multirow{2}{*}{Shift}   & \multicolumn{4}{|c||}{Single-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, No Center Loss} & \multicolumn{4}{|c||}{Multi-Head, Center Loss} \\
            & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   & AUROC & HOS   & UNK   & OS*   \\
    \hline
    A$\to$C & 52.07 & 44.76 & 58.65 & 36.19 & 57.46 & 46.64 & 62.95 & 37.04 & 59.77 & 52.68 & 62.73 & 45.40 \\
    A$\to$P & 50.84 & 51.27 & 57.56 & 46.23 & 56.31 & 54.13 & 60.42 & 49.03 & 56.86 & 52.46 & 63.35 & 44.77 \\
    A$\to$R & 27.94 & 68.13 & 17.58 & 52.25 & 59.88 & 56.60 & 53.18 & 60.65 & 58.86 & 61.67 & 66.82 & 57.26 \\
    C$\to$A & 49.52 & 41.74 & 43.10 & 40.47 & 55.28 & 42.63 & 51.57 & 36.33 & 55.76 & 46.84 & 60.19 & 38.35 \\
    C$\to$P & 54.42 & 46.99 & 41.51 & 54.15 & 59.13 & 51.88 & 60.03 & 45.69 & 58.35 & 52.69 & 62.19 & 45.72 \\
    C$\to$R & 53.43 & 46.18 & 38.64 & 57.39 & 60.75 & 56.00 & 61.29 & 51.63 & 59.15 & 55.97 & 63.18 & 50.25 \\
    P$\to$A & 48.32 & 37.07 & 33.70 & 41.20 & 55.62 & 41.72 & 48.90 & 36.39 & 53.50 & 40.97 & 49.53 & 34.94 \\
    P$\to$C & 47.76 & 43.99 & 48.42 & 40.31 & 56.77 & 46.10 & 55.11 & 39.65 & 58.64 & 46.81 & 60.95 & 37.99 \\
    P$\to$R & 50.37 & 34.14 & 22.88 & 67.27 & 59.68 & 48.41 & 40.91 & 59.30 & 61.10 & 56.22 & 56.89 & 55.58 \\
    R$\to$A & 49.39 & 25.08 & 15.99 & 58.19 & 58.47 & 45.00 & 39.50 & 52.43 & 57.98 & 48.92 & 45.61 & 52.77 \\
    R$\to$C & 49.80 & 46.70 & 48.27 & 45.23 & 57.02 & 49.00 & 42.82 & 57.34 & 57.09 & 48.69 & 61.11 & 40.47 \\
    R$\to$P & 54.10 & 23.37 & 13.89 & 73.69 & 62.33 & 50.31 & 39.51 & 69.27 & 63.96 & 59.64 & 54.40 & 66.02 \\
    \hline
    AVG     & 49.00 & 42.45 & 36.68 & 51.05 & 58.23 & 49.03 & 51.35 & 49.56 & 58.42 & 51.96 & 58.91 & 47.46 \\ 
    \hline
  \end{tabular}
  \caption{\centering\label{tab:results}Final results for the three configurations on all domain shifts. All values are percentages.}
\end{table*}
